\section{Test Methods}
There are a number of different types of tests appropriate for our project. The tests mentioned in this chapter are general tests that works equally well on software development and hardware related development. 


\subsection{Static Testing}
The primary purpose of Static Testing or Static Verification is to find errors in documentation and code. We do this through review, analysis, inspection, and walk-through. The purpose of this is to find deviations from the stakeholders need. The results can be used to optimize development process and provide input to the dynamic testing \cite{ref3}. 

\subsection{Dynamic Testing}
Dynamic Testing can be conducted on the actual product. The purpose of this is to find deviations from expected values or the confirmed values \cite{ref3}. The main purpose of Dynamic Testing is to ensure consistency of the system.

\subsubsection{Black Box Testing}
In Black Box Testing the internal structure, design or code is not known to the tester. The main aspiration is to verify the functionality of the system under test and that this translates back to the criteria. 


\paragraph{Functional Testing} \\
Functional Testing is conducted to verify that the features developed for our systems are according to the functional Backlog Item. The tests are performed based on the Acceptance Criteria written by the Scrum Team or Tester. In Functional Testing is tested by providing input, verifying the output and comparing the actual results with the expected results.\\
\\
There different levels of Functional Testing 

\paragraph{Non-Functional Testing} \\
Non-Functional Testing is a testing technique which does not focus on functional aspects of the system. It mainly focuses on the Non-Functional characteristics of the system such as performance, robustness and stability. Non-Functional testing is performed at all test levels \cite{ref6}.

\subsubsection{White Box Testing}
White Box Testing is a method in which the internal structure or workings of a system is tested. This type of testing is mostly used in software developing and the goal of White Box testing is to check how a system is performing based on the code. This type of test is mostly conducted by a Team Member who has knowledge in programming and the advantage of this is that the tests can analyze the structure and find the number of test scenarios that are necessary to ensure detection of flaws and errors in the system. 